---
title: "glmhmm metacognition plots"
output: html_notebook
---

```{r}
library(reticulate)
use_condaenv("glmhmm")

source_python("python/glm_hmm.py")
```

```{python}
import numpy as np
import numpy.random as npr
import matplotlib.pyplot as plt
import ssm 
```

```{r}
library(tidyverse)
library(broom)
library(dplyr)
library(R.matlab)
library(flexplot)
library(cowplot)
library(purrr)
library(ggforce)

list.files("R", full.names = TRUE) |> 
  walk(source)
```


----------------------------------------------------------------------
----------------------------------------------------------------------
INDIVIDUAL MODEL PLOTTING
----------------------------------------------------------------------
----------------------------------------------------------------------


```{r}
load("RData/data_trials.RData")
```

```{r}
load("RData/m1_prec.RData")
# load("RData/m1_52.RData")
# load("RData/m1_104.RData")
# load("RData/m1_156.RData")

load("RData/m2_prec.RData")
# load("RData/m2_52.RData")
# load("RData/m2_104.RData")
# load("RData/m2_156.RData")

load("RData/m3_prec.RData")
# load("RData/m3_52.RData")
# load("RData/m3_104.RData")
# load("RData/m3_156.RData")

load("RData/m4_prec.RData")
# load("RData/m4_52.RData")
# load("RData/m4_104.RData")
# load("RData/m4_156.RData")
```

Functions and labels to plot each model of each subject:
```{r}
# Wrapper functions
plotting_psycho_one_participant_with_labels <- function(fit, labels) {
  plot <- plotting_psycho_one_participant(fit)
  plot + labs(x = labels[1], y = labels[2])
}

plotting_trials_one_participant_with_labels <- function(fit, labels) {
  plot <- plotting_trials_one_participant(fit)
  plot + labs(x = labels[1], y = labels[2])
}

# Define your labels here
labels1 <- c("Dot difference", "Probability right")
labels2 <- c("Trial", "Probability state")
```

Plotting one state:
```{r}
plots_1 <- m1_prec[m1_prec$subject %in% unique(m1_prec$subject)[1:10], ] %>% 
  rowwise() %>% 
  mutate(p = list(plot_grid(
    plotting_psycho_one_participant_with_labels(fit, labels1), 
    plotting_trials_one_participant_with_labels(fit, labels2),
    labels = subject,
    label_x = .15, label_y = .95, 
    rel_widths = c(.5, .5)
  ))) 

plots_1_grid <- plot_grid(plotlist = plots_1$p, ncol = 2) 

file_name <- paste0("figures/", deparse(substitute(.glm_hmm)), ".pdf")

ggsave("figures/plots_1_grid.pdf", plots_1_grid, width = 15, height = 15)
```

Plotting two states:
```{r}
plots_2 <- m2_prec[m2_prec$subject %in% unique(m2_prec$subject)[1:10], ] %>% 
  rowwise() %>% 
  mutate(p = list(plot_grid(
    plotting_psycho_one_participant_with_labels(fit, labels1), 
    plotting_trials_one_participant_with_labels(fit, labels2),
    labels = subject,
    label_x = .15, label_y = .95, 
    rel_widths = c(.5, .5)
  ))) 

plots_2_grid <- plot_grid(plotlist = plots_2$p, ncol = 2) 

file_name <- paste0("figures/", deparse(substitute(.glm_hmm)), ".pdf")

ggsave("figures/plots_2_grid.pdf", plots_2_grid, width = 15, height = 15)
```

Plotting three states:
```{r}
plots_3 <- m3_prec[m3_prec$subject %in% unique(m3_prec$subject)[1:10], ] %>% 
  rowwise() %>% 
  mutate(p = list(plot_grid(
    plotting_psycho_one_participant_with_labels(fit, labels1), 
    plotting_trials_one_participant_with_labels(fit, labels2),
    labels = subject,
    label_x = .15, label_y = .95, 
    rel_widths = c(.5, .5)
  ))) 

plots_3_grid <- plot_grid(plotlist = plots_3$p, ncol = 2) 

file_name <- paste0("figures/", deparse(substitute(.glm_hmm)), ".pdf")

ggsave("figures/plots_3_grid.pdf", plots_3_grid, width = 15, height = 15)
```

Plotting four states:
```{r}
plots_4 <- m4_prec[m4_prec$subject %in% unique(m4_prec$subject)[1:10], ] %>% 
  rowwise() %>% 
  mutate(p = list(plot_grid(
    plotting_psycho_one_participant_with_labels(fit, labels1), 
    plotting_trials_one_participant_with_labels(fit, labels2),
    labels = subject,
    label_x = .15, label_y = .95, 
    rel_widths = c(.5, .5)
  ))) 

plots_4_grid <- plot_grid(plotlist = plots_4$p, ncol = 2) 

file_name <- paste0("figures/", deparse(substitute(.glm_hmm)), ".pdf")

ggsave("figures/plots_4_grid.pdf", plots_4_grid, width = 15, height = 15)
```


----------------------------------------------------------------------
Subject 5 
----------------------------------------------------------------------


```{r}
PARTICIPANT <- 5
REL_WIDTHS <- c(.4, .5)
```

```{r}
plots_1_one_participant <- m1_prec[m1_prec$subject %in% unique(m1_prec$subject)[PARTICIPANT], ] %>% 
  rowwise() %>% 
  mutate(p = list(plot_grid(
    plotting_psycho_one_participant_with_labels(fit, labels1) +
      scale_color_discrete(name = "States",
                       labels = "1"), 
    plotting_trials_one_participant_with_labels(fit, labels2) +
      scale_color_discrete(name = "States",
                       labels = "1"),
    #labels = paste("Participant", subject),
    label_x = .08, label_y = .95, label_size = 10, 
    rel_widths = REL_WIDTHS
  ))) 

plots_1_grid_one_participant <- plot_grid(plotlist = plots_1_one_participant$p) 

plots_1_grid_one_participant
```

```{r}
plots_2_one_participant <- m2_prec[m2_prec$subject %in% unique(m2_prec$subject)[PARTICIPANT], ] %>% 
  rowwise() %>% 
  mutate(p = list(plot_grid(
    plotting_psycho_one_participant_with_labels(fit, labels1) +
      scale_color_discrete(name = "States",
                       labels = c("1", "2")), 
    plotting_trials_one_participant_with_labels(fit, labels2) +
      scale_color_discrete(name = "States",
                       labels = c("1", "2")),
    #labels = paste("Participant", subject),
    label_x = .08, label_y = .95, label_size = 10, 
    rel_widths = REL_WIDTHS
  ))) 

plots_2_grid_one_participant <- plot_grid(plotlist = plots_2_one_participant$p) 

plots_2_grid_one_participant
```

```{r}
plots_3_one_participant <- m3_prec[m3_prec$subject %in% unique(m3_prec$subject)[PARTICIPANT], ] %>% 
  rowwise() %>% 
  mutate(p = list(plot_grid(
    plotting_psycho_one_participant_with_labels(fit, labels1) +
      scale_color_discrete(name = "States",
                       labels = c("1", "2", "3")), 
    plotting_trials_one_participant_with_labels(fit, labels2) +
      scale_color_discrete(name = "States",
                       labels = c("1", "2", "3")),
    #labels = paste("Participant", subject),
    label_x = .08, label_y = .95, label_size = 10, 
    rel_widths = REL_WIDTHS
  ))) 

plots_3_grid_one_participant <- plot_grid(plotlist = plots_3_one_participant$p) 

plots_3_grid_one_participant
```

```{r}
plots_4_one_participant <- m4_prec[m4_prec$subject %in% unique(m4_prec$subject)[PARTICIPANT], ] %>% 
  rowwise() %>% 
  mutate(p = list(plot_grid(
    plotting_psycho_one_participant_with_labels(fit, labels1) +
      scale_color_discrete(name = "States",
                       labels = c("1", "2", "3", "4")), 
    plotting_trials_one_participant_with_labels(fit, labels2) +
      scale_color_discrete(name = "States",
                       labels = c("1", "2", "3", "4")),
    #labels = paste("Participant", subject),
    label_x = .08, label_y = .95, label_size = 10, 
    rel_widths = REL_WIDTHS
  ))) 

plots_4_grid_one_participant <- plot_grid(plotlist = plots_4_one_participant$p) 

plots_4_grid_one_participant
```

```{r}
plots_one_participant <- plot_grid(
  plots_1_grid_one_participant,
  plots_2_grid_one_participant, 
  plots_3_grid_one_participant,
  plots_4_grid_one_participant, 
  ncol = 1, labels = "AUTO"
)

plots_one_participant

ggsave("figures/plots_one_participant.pdf", plots_one_participant, 
       height = 8, width = 7)
```


----------------------------------------------------------------------
----------------------------------------------------------------------
SUBJECT DISTRIBUTION OF BEST MODEL 
----------------------------------------------------------------------
----------------------------------------------------------------------


```{r}
load("RData/liks_all_best.RData")
load("RData/liks_52_best.RData")
load("RData/liks_104_best.RData")
load("RData/liks_156_best.RData")
```

Including all trials
```{r}
plot_dist_best <- liks_all_best |> 
  group_by(model) |> 
  count() |> 
  mutate(model = recode(model, 
                        `int-slo 1` = "1 state", 
                        `int-slo 2` = "2 states", 
                        `int-slo 3` = "3 states", 
                        `int-slo 4` = "4 states", 
                        )) |> 
  ggplot(aes(x = model, y = n)) +
  geom_col() +
  scale_fill_brewer(palette = "Set1", type = "qual") +
  theme(legend.position = "none", 
        axis.title.x = element_blank()) +
  labs(y = "Number of participants")

plot_dist_best

ggsave("figures/plot_dist_best.pdf", plot_dist_best, width = 3, height = 2.5)
```

First 52 trials
```{r}
plot_dist_best_52 <- liks_52_best |> 
  group_by(model) |> 
  count() |> 
  mutate(model = recode(model, 
                        `int-slo 1` = "1 state", 
                        `int-slo 2` = "2 states", 
                        `int-slo 3` = "3 states", 
                        `int-slo 4` = "4 states", 
                        )) |> 
  ggplot(aes(x = model, y = n)) +
  geom_col() +
  scale_fill_brewer(palette = "Set1", type = "qual") +
  theme(legend.position = "none", 
        axis.title.x = element_blank()) +
  labs(y = "Number of participants")

plot_dist_best_52

ggsave("figures/plot_dist_best_52.pdf", plot_dist_best_52, width = 3, height = 2.5)
```

First 104 trials
```{r}
plot_dist_best_104 <- liks_104_best |> 
  group_by(model) |> 
  count() |> 
  mutate(model = recode(model, 
                        `int-slo 1` = "1 state", 
                        `int-slo 2` = "2 states", 
                        `int-slo 3` = "3 states", 
                        `int-slo 4` = "4 states", 
                        )) |> 
  ggplot(aes(x = model, y = n)) +
  geom_col() +
  scale_fill_brewer(palette = "Set1", type = "qual") +
  theme(legend.position = "none", 
        axis.title.x = element_blank()) +
  labs(y = "Number of participants")

plot_dist_best_104

ggsave("figures/plot_dist_best_104.pdf", plot_dist_best_104, width = 3, height = 2.5)
```

First 156 trials
```{r}
plot_dist_best_156 <- liks_156_best |> 
  group_by(model) |> 
  count() |> 
  mutate(model = recode(model, 
                        `int-slo 1` = "1 state", 
                        `int-slo 2` = "2 states", 
                        `int-slo 3` = "3 states", 
                        `int-slo 4` = "4 states", 
                        )) |> 
  ggplot(aes(x = model, y = n)) +
  geom_col() +
  scale_fill_brewer(palette = "Set1", type = "qual") +
  theme(legend.position = "none", 
        axis.title.x = element_blank()) +
  labs(y = "Number of participants")

plot_dist_best_156

ggsave("figures/plot_dist_best_156.pdf", plot_dist_best_156, width = 3, height = 2.5)
```


```{r}
dist_diff_trials <- plot_grid(
  plot_dist_best_52, 
  plot_dist_best_104,
  plot_dist_best_156,
  plot_dist_best,
  ncol = 2, labels = "AUTO"
)

dist_diff_trials

ggsave("figures/dist_diff_trials.pdf", dist_diff_trials, 
       height = 7, width = 8)
```


----------------------------------------------------------------------
----------------------------------------------------------------------
DWELL TIME DISTRIBUTION
----------------------------------------------------------------------
----------------------------------------------------------------------


```{r}
load("RData")
```



----------------------------------------------------------------------
----------------------------------------------------------------------
CONFIDENCE
----------------------------------------------------------------------
----------------------------------------------------------------------


----------------------------------------------------------------------
States ordered based on precision
----------------------------------------------------------------------


```{r}
load("RData/m1_conf_prec_sub.RData")
load("RData/m2_conf_prec_sub.RData")
load("RData/m3_conf_prec_sub.RData")
load("RData/m4_conf_prec_sub.RData")
```


Define a custom function to calculate the confidence interval
```{r}
calculate_ci <- function(x) {
  mean_val <- mean(x)
  n <- length(x)
  se <- sd(x) / sqrt(n)
  margin_error <- qt(0.975, df = n - 1) * se
  ci_inf <- mean_val - margin_error
  ci_sup <- mean_val + margin_error
  return(as.numeric(c(ci_inf, ci_sup)))
}
```

1S model (Bruno):
```{r}
ci_conf_prec_m1 <- calculate_ci(m1_conf_prec_sub$mean_confidence) |>
                                  t()

ci_conf_prec_m1 <- data.frame(
  ci_inf = ci_conf_prec_m1[, 1],
  ci_sup = ci_conf_prec_m1[, 2]
)

# Create a new dataframe with group, mean, and confidence intervals
result_conf_prec_1S <- as.data.frame(ci_conf_prec_m1) |>
  mutate(mean = (ci_inf + ci_sup)/2) 

means_conf_prec_m1_plot <- ggplot() +
  geom_sina(data = m1_conf_prec_sub, aes(x = 1, y = mean_confidence), binwidth = .02, maxwidth = .3, size = .75) +
  geom_crossbar(data = result_conf_prec_1S, size = .30, width = 0.3, aes(x = 1, y = mean, ymin = ci_inf, ymax = ci_sup, color = "red")) +
  labs(x = "Single state", y = "Confidence") +
  theme_gray() +
   theme(legend.position = "none",
     strip.background = element_blank(),
     axis.line = element_line(size = .25), 
     axis.ticks = element_blank(),
     axis.text.x = element_blank()) +
  ylim(0, 11)

ggsave("figures/means_conf_prec_m1_plot.pdf", plot = means_conf_prec_m1_plot)

means_conf_prec_m1_plot
```

```{r}
SIZE_POINT <- 0.4
ALPHA <- 0.15
```

1S model:
CREO QUE HAY ALGO MAL EN EL CÁLCULO DE LOS CIS.
```{r}
n_m1_prec <- length(m1_conf_prec_sub)
se_m1_prec <- mean(m1_conf_prec_sub$sd_confidence / sqrt(n_m1_prec))
margin_error_m1_prec <- mean(qt(0.975, df = n_m1_prec - 1) * se_m1_prec)
ci_inf_m1_prec <- mean(m1_conf_prec_sub$mean_confidence - margin_error_m1_prec)
ci_sup_m1_prec <- mean(m1_conf_prec_sub$mean_confidence + margin_error_m1_prec)
mean_m1_prec <- mean(m1_conf_prec_sub$mean_confidence)

means_conf_prec_m1_plot <- ggplot() +
  geom_sina(data = m1_conf_prec_sub, aes(x = "S1", y = mean_confidence), binwidth = .02, maxwidth = .5, size = SIZE_POINT, alpha = ALPHA) +
  geom_crossbar(size = .10, width = 0.2, aes(x = "S1", y = mean_m1_prec, ymin = ci_inf_m1_prec, ymax = ci_sup_m1_prec)) +
   scale_color_brewer(palette = "Set1", type = "qual") +
  labs(x = " ", y = "Confidence") +
  theme_classic() +
   theme(legend.position = "none",
     strip.background = element_blank(),
     axis.title.x = element_blank(),
           axis.line = element_line(size = .25), 
         axis.ticks = element_line(size = .25))

ggsave("figures/means_conf_prec_m1_plot.pdf")

means_conf_prec_m1_plot
```

2S model:
(Subject 11 had a mean confidience of 11 and a sd of 0)
```{r}
means_conf_prec_m2 <- aggregate(mean_confidence ~ state, data = m2_conf_prec_sub, FUN = mean)
ci_conf_prec_m2 <- aggregate(mean_confidence ~ state, data = m2_conf_prec_sub, FUN = function(x) t.test(x)$conf.int)

result_conf_prec_2S <- merge(means_conf_prec_m2, ci_conf_prec_m2, by = "state")

means_conf_prec_m2_plot <- ggplot() +
  geom_sina(data = m2_conf_prec_sub, aes(x = state, y = mean_confidence, color = state), binwidth = .02, maxwidth = .5, size = SIZE_POINT, alpha = ALPHA) +
  geom_crossbar(data = result_conf_prec_2S, size = .30, width = 0.5, aes(x = state, y = mean_confidence.x, ymin = mean_confidence.y[,1], ymax = mean_confidence.y[,2], color = state)) +
   scale_color_brewer(palette = "Set1", type = "qual") +
  labs(x = "State", y = "Confidence") +
  theme_classic() +
   theme(legend.position = "none",
     strip.background = element_blank(),
     axis.title.x = element_blank(),
           axis.line = element_line(size = .25), 
         axis.ticks = element_line(size = .25))

ggsave("figures/means_conf_prec_m2_plot.pdf")

means_conf_prec_m2_plot
```

3S model:
```{r}
ci_conf_prec_m3 <- sapply(
  split(m3_conf_prec_sub$mean_confidence, m3_conf_prec_sub$state),
  function(x) {
    result <- calculate_ci(x)
    print(result)
    result
  }
)
ci_conf_prec_m3 <- t(ci_conf_prec_m3)

ci_conf_prec_m3 <- data.frame(
  state = rownames(ci_conf_prec_m3),
  ci_inf = ci_conf_prec_m3[, 1],
  ci_sup = ci_conf_prec_m3[, 2]
)

# Create a new dataframe with group, mean, and confidence intervals
result_conf_prec_3S <- as.data.frame(ci_conf_prec_m3) |>
  group_by(state) |>
  mutate(mean = (ci_inf + ci_sup)/2)

result_conf_prec_3S

means_conf_prec_m3_plot <- ggplot() +
  geom_sina(data = m3_conf_prec_sub, aes(x = state, y = mean_confidence, color = state), binwidth = .02, maxwidth = .5, size = SIZE_POINT, alpha = ALPHA) +
  geom_crossbar(data = result_conf_prec_3S, size = .30, width = 0.5, aes(x = state, y = mean, ymin = ci_inf, ymax = ci_sup, color = state)) +
  labs(x = "State", y = "Confidence") +
   scale_color_brewer(palette = "Set1", type = "qual") +
  theme_classic() +
   theme(legend.position = "none",
     strip.background = element_blank(),
     axis.title.x = element_blank(),
           axis.line = element_line(size = .25), 
         axis.ticks = element_line(size = .25))

ggsave("figures/means_conf_prec_m3_plot.pdf")

means_conf_prec_m3_plot
```


4S model:
```{r}
ci_conf_prec_m4 <- sapply(
  split(m4_conf_prec_sub$mean_confidence, m4_conf_prec_sub$state),
  function(x) {
    result <- calculate_ci(x)
    print(result)
    result
  }
)
ci_conf_prec_m4 <- t(ci_conf_prec_m4)

ci_conf_prec_m4 <- data.frame(
  state = rownames(ci_conf_prec_m4),
  ci_inf = ci_conf_prec_m4[, 1],
  ci_sup = ci_conf_prec_m4[, 2]
)

# Create a new dataframe with group, mean, and confidence intervals
result_conf_prec_4S <- as.data.frame(ci_conf_prec_m4) |>
  group_by(state) |>
  mutate(mean = (ci_inf + ci_sup)/2)

result_conf_prec_4S

means_conf_prec_m4_plot <- ggplot() +
  geom_sina(data = m4_conf_prec_sub, aes(x = state, y = mean_confidence, color = state), binwidth = .02, maxwidth = .5, size = SIZE_POINT, alpha = ALPHA) +
  geom_crossbar(data = result_conf_prec_4S, size = .30, width = 0.5, aes(x = state, y = mean, ymin = ci_inf, ymax = ci_sup, color = state)) +
  labs(x = "State", y = "Confidence") +
    scale_color_brewer(palette = "Set1", type = "qual") +
  theme_classic() +
   theme(legend.position = "none",
     strip.background = element_blank(),
     axis.title.x = element_blank(),
           axis.line = element_line(size = .25), 
         axis.ticks = element_line(size = .25))

ggsave("figures/means_conf_prec_m4_plot.pdf")

means_conf_prec_m4_plot
```

Por el momento no incluyo el de un solo estado, porque hay que arreglarlo
```{r}
Y_LIMIT_SUP <- 9.5
Y_LIMIT_INF <- 6.5

p_confidence <- plot_grid(
  #eans_conf_prec_m1_plot + coord_cartesian(ylim = c(Y_LIMIT_INF, Y_LIMIT_SUP)),
   means_conf_prec_m2_plot + coord_cartesian(ylim = c(Y_LIMIT_INF, Y_LIMIT_SUP)),
  means_conf_prec_m3_plot + coord_cartesian(ylim = c(Y_LIMIT_INF, Y_LIMIT_SUP)),
  means_conf_prec_m4_plot + coord_cartesian(ylim = c(Y_LIMIT_INF, Y_LIMIT_SUP)), 
  nrow = 1, 
  labels = "AUTO",
  rel_widths = c(.2, .25, .4))
  #COn todos los modelos: rel_widths = c(.15, .2, .25, .4))

p_confidence

ggsave("figures/p_confidence.pdf", p_confidence, width = 7, height = 2)
```


----------------------------------------------------------------------
States ordered based on bias
----------------------------------------------------------------------


```{r}
load("RData/m1_conf_bias_sub.RData")
load("RData/m2_conf_bias_sub.RData")
load("RData/m3_conf_bias_sub.RData")
load("RData/m4_conf_bias_sub.RData")
```

1S model:
CREO QUE HAY ALGO MAL EN EL CÁLCULO DE LOS CIS.
```{r}
n_m1_bias <- length(m1_conf_bias_sub)
se_m1_bias <- mean(m1_conf_bias_sub$sd_confidence / sqrt(n_m1_bias))
margin_error_m1_bias <- mean(qt(0.975, df = n_m1_bias - 1) * se_m1_bias)
ci_inf_m1_bias <- mean(m1_conf_bias_sub$mean_confidence - margin_error_m1_bias)
ci_sup_m1_bias <- mean(m1_conf_bias_sub$mean_confidence + margin_error_m1_bias)
mean_m1_bias <- mean(m1_conf_bias_sub$mean_confidence)

means_conf_bias_m1_plot <- ggplot() +
  geom_sina(data = m1_conf_bias_sub, aes(x = "S1", y = mean_confidence), binwidth = .02, maxwidth = .5, size = SIZE_POINT, alpha = ALPHA) +
  geom_crossbar(size = .10, width = 0.2, aes(x = "S1", y = mean_m1_bias, ymin = ci_inf_m1_bias, ymax = ci_sup_m1_bias)) +
   scale_color_brewer(palette = "Set1", type = "qual") +
  labs(x = " ", y = "Confidence") +
  theme_classic() +
   theme(legend.position = "none",
     strip.background = element_blank(),
     axis.title.x = element_blank(),
           axis.line = element_line(size = .25), 
         axis.ticks = element_line(size = .25))

ggsave("figures/means_conf_bias_m1_plot.pdf")

means_conf_bias_m1_plot
```

2S model:
(Subject 11 had a mean confidience of 11 and a sd of 0)
```{r}
means_conf_bias_m2 <- aggregate(mean_confidence ~ state, data = m2_conf_bias_sub, FUN = mean)
ci_conf_bias_m2 <- aggregate(mean_confidence ~ state, data = m2_conf_bias_sub, FUN = function(x) t.test(x)$conf.int)

result_conf_bias_2S <- merge(means_conf_bias_m2, ci_conf_bias_m2, by = "state")

means_conf_bias_m2_plot <- ggplot() +
  geom_sina(data = m2_conf_bias_sub, aes(x = state, y = mean_confidence, color = state), binwidth = .02, maxwidth = .5, size = SIZE_POINT, alpha = ALPHA) +
  geom_crossbar(data = result_conf_bias_2S, size = .30, width = 0.5, aes(x = state, y = mean_confidence.x, ymin = mean_confidence.y[,1], ymax = mean_confidence.y[,2], color = state)) +
   scale_color_brewer(palette = "Set1", type = "qual") +
  labs(x = "State", y = "Confidence") +
  theme_classic() +
   theme(legend.position = "none",
     strip.background = element_blank(),
     axis.title.x = element_blank(),
           axis.line = element_line(size = .25), 
         axis.ticks = element_line(size = .25))

ggsave("figures/means_conf_bias_m2_plot.pdf")

means_conf_bias_m2_plot
```

3S model:
```{r}
ci_conf_bias_m3 <- sapply(
  split(m3_conf_bias_sub$mean_confidence, m3_conf_bias_sub$state),
  function(x) {
    result <- calculate_ci(x)
    print(result)
    result
  }
)
ci_conf_bias_m3 <- t(ci_conf_bias_m3)

ci_conf_bias_m3 <- data.frame(
  state = rownames(ci_conf_bias_m3),
  ci_inf = ci_conf_bias_m3[, 1],
  ci_sup = ci_conf_bias_m3[, 2]
)

# Create a new dataframe with group, mean, and confidence intervals
result_conf_bias_3S <- as.data.frame(ci_conf_bias_m3) |>
  group_by(state) |>
  mutate(mean = (ci_inf + ci_sup)/2)

result_conf_bias_3S

means_conf_bias_m3_plot <- ggplot() +
  geom_sina(data = m3_conf_bias_sub, aes(x = state, y = mean_confidence, color = state), binwidth = .02, maxwidth = .5, size = SIZE_POINT, alpha = ALPHA) +
  geom_crossbar(data = result_conf_bias_3S, size = .30, width = 0.5, aes(x = state, y = mean, ymin = ci_inf, ymax = ci_sup, color = state)) +
  labs(x = "State", y = "Confidence") +
   scale_color_brewer(palette = "Set1", type = "qual") +
  theme_classic() +
   theme(legend.position = "none",
     strip.background = element_blank(),
     axis.title.x = element_blank(),
           axis.line = element_line(size = .25), 
         axis.ticks = element_line(size = .25))

ggsave("figures/means_conf_bias_m3_plot.pdf")

means_conf_bias_m3_plot
```


4S model:
```{r}
ci_conf_bias_m4 <- sapply(
  split(m4_conf_prec_sub$mean_confidence, m4_conf_bias_sub$state),
  function(x) {
    result <- calculate_ci(x)
    print(result)
    result
  }
)
ci_conf_bias_m4 <- t(ci_conf_bias_m4)

ci_conf_bias_m4 <- data.frame(
  state = rownames(ci_conf_bias_m4),
  ci_inf = ci_conf_bias_m4[, 1],
  ci_sup = ci_conf_bias_m4[, 2]
)

# Create a new dataframe with group, mean, and confidence intervals
result_conf_bias_4S <- as.data.frame(ci_conf_bias_m4) |>
  group_by(state) |>
  mutate(mean = (ci_inf + ci_sup)/2)

result_conf_bias_4S

means_conf_bias_m4_plot <- ggplot() +
  geom_sina(data = m4_conf_bias_sub, aes(x = state, y = mean_confidence, color = state), binwidth = .02, maxwidth = .5, size = SIZE_POINT, alpha = ALPHA) +
  geom_crossbar(data = result_conf_bias_4S, size = .30, width = 0.5, aes(x = state, y = mean, ymin = ci_inf, ymax = ci_sup, color = state)) +
  labs(x = "State", y = "Confidence") +
    scale_color_brewer(palette = "Set1", type = "qual") +
  theme_classic() +
   theme(legend.position = "none",
     strip.background = element_blank(),
     axis.title.x = element_blank(),
           axis.line = element_line(size = .25), 
         axis.ticks = element_line(size = .25))

ggsave("figures/means_conf_bias_m4_plot.pdf")

means_conf_bias_m4_plot
```

Por el momento no incluyo el de un solo estado, porque hay que arreglarlo
```{r}
Y_LIMIT_SUP <- 9.5
Y_LIMIT_INF <- 6.5

b_confidence <- plot_grid(
  #eans_conf_bias_m1_plot + coord_cartesian(ylim = c(Y_LIMIT_INF, Y_LIMIT_SUP)),
   means_conf_bias_m2_plot + coord_cartesian(ylim = c(Y_LIMIT_INF, Y_LIMIT_SUP)),
  means_conf_bias_m3_plot + coord_cartesian(ylim = c(Y_LIMIT_INF, Y_LIMIT_SUP)),
  means_conf_bias_m4_plot + coord_cartesian(ylim = c(Y_LIMIT_INF, Y_LIMIT_SUP)), 
  nrow = 1, 
  labels = "AUTO",
  rel_widths = c(.2, .25, .4))
  #COn todos los modelos: rel_widths = c(.15, .2, .25, .4))

b_confidence

ggsave("figures/b_confidence.pdf", b_confidence, width = 7, height = 2)
```






